%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  % \cventry
  %   {Production Engineer} % Job title
  %   {Facebook} % Organization
  %   {Menlo Park, CA}
  %   {September 2020 - } % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \end{cvitems}
  %   }
  \cventry
  {Software Engineer (Voulenteer)} % Job title
    {Covid Watch} % Organization
    {The Internet}
    {March 2020 - September 2020 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Covid Watch is a non-profit who builds a privacy-focused exposure notification system. Through a mobile app, the system alerts users to possible COVID-19 exposures. The system is currently used by universities in the state of Arizona, with more locations coming soon.}
      \item{Collaborated with teammates across the world in a startup-like environment.}
      \item {Helped develop the organization's website and a React web app used by health authorities to verify diagnoses. The work was open source and the web app can be found at https://github.com/covidwatchorg/portal.}
      \item {Wrote CI/CD pipelines and managed AWS distributions.}
      \end{cvitems}
    }

   \cventry
    {Computer Science Lab Coach}
    {Vassar College}
    {Poughkeepsie, NY}
    {August 2017 - May 2020}
    {
        \begin{cvitems}
        \item {Assisted in laboratory sessions for classes \textit{Operating Systems}, \textit{Data Structures and Algorithms} (Intro to Java), and \textit{Problem Solving and Abstraction} (Intro to CS in Scheme).}        
        \item {Held personal office hours 9 hours per week for students who required help.}
        \item {Gave students real-time feedback on their code and explained larger concepts such operating systems theory, object-oriented programming, and data structures.}
        \end{cvitems}
    }
  \cventry
    {Production Engineer Intern} % Job title
    {Facebook} % Organization
    {Menlo Park, CA} % Location
    {June 2019 - August 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked on the Real-Time Infrastructure team.}
      \item {Projects included a debugging feature and implementing A/B tests to assess the quality of a migration. Primarily worked in C++ and Python.} 
      \item {Learned the challenges of building and maintaining services at a large scale.}
      \end{cvitems}
    }

  \cventry
    {DevOps Developer Intern} % Job title
    {IBM} % Organization
    {Poughkeepsie, NY} % Location
    {June 2018 - August 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked in the IBM Z Innovation Lab.}
        \item {Learned modern DevOps and cloud computing tools such as Docker, Kubernetes, and OpenShift.}
        \item {Presented final projects to executives at intern finale event.}
      \end{cvitems}
    }

    \cventry
    {Research Assistant}
    {Vassar College}
    {Poughkeepsie, NY}
    {November 2016 - November 2017}
    {
        \begin{cvitems}
        \item{Worked with professor Pavel Naumov to improve and generalize an existing model of Diffusion in Social Networks. Proved our model’s consistency and completeness.}
        \item{Published paper “Group Conformity” to the Journal of Logic, Language and Information.} 
        \end{cvitems}
        }

\end{cventries}
